### 2017-04-30 thesis/latex/thesis.tex
Add input parameters to thesis.

\begin{figure}[H]
  \centering
  \includegraphics[width=0.2\textwidth]{../../plots/stepping-ghost}
  \caption{Snapshots of model over the course of a simulation. Bothbound states are depicted immediately after binding events. Onebound states depict the conformation with the highest unbound binding domain between binding events. Simulation run at standard conditions with $k_b=123 s^{-1}, k_{ub}=456 s^{-1}, c_b=c_m=c_t=789 \Delta G_{ATP}$.}
  \label{fig:stepping-ghosts}
\end{figure}

@@

\begin{figure}[H]
  \centering
    \includegraphics[width=0.5\textwidth]{../../plots/stepping_length_histogram_thesis}%%
    \includegraphics[width=0.5\textwidth]{../../plots/stepping_time_histogram_thesis}
    \includegraphics[width=0.5\textwidth]{../../figures/weihong-step-size.pdf}%%
    \includegraphics[width=0.5\textwidth]{../../figures/weihong-velocity.pdf}
    \caption{Experimental dynein step time from \cite{weihongpaper}}
    \label{fig:final-histograms}
\end{figure}

>>>>

\begin{figure}[h]
  \centering
  \begin{tabular}{| l | l | l | l | l |}
    \hline
    $k_{b}$ & $k_{ub}$ & $c_b$ &  $c_m$ & $c_t$\\\hline
    $10^{18} s^{-1}$ & $10^{20} s^{-1}$ & $2.0\Delta G_{ATP}$ & $2.0\Delta G_{ATP}$ & $1.0\Delta G_{ATP}$\\ \hline
  \end{tabular}
  \caption{Parameters used in simulations.}
  \label{table:thesis-parameters}
\end{figure}

@@

\begin{figure}[H]
  \centering
    \includegraphics[width=0.5\textwidth]{../../plots/stepping_length_histogram_thesis}%%
    \includegraphics[width=0.5\textwidth]{../../figures/weihong-step-size.pdf}
    \caption{Model vs experimental step sizes. \textbf{a.)} Step sizes model took at parameters in \ref{table:thesis-parameters}. \textbf{b.)} Experimental stepping behavior of dynein \cite{weihongpaper}.}
    \label{fig:final-histograms}
\end{figure}
